Reproducible Research - Project 1
========================================================

Reading in data and calculating the total number of steps per day, mean and median steps per day

```{r}
activity<-read.csv("activity.csv")
StepsPerDay<-tapply(activity$steps,activity$date,sum,na.rm=TRUE)
```

Plotting Average Steps per day

```{r fig.width=7, fig.height=6}
hist(StepsPerDay,xlab="Steps Per Day",ylab = "Number of Days",ylim=c(0,30),main="Steps Per Day")
```

calculating Mean and Median Steps per day
```{r}
meanSteps<-mean(StepsPerDay,na.rm=TRUE)
medianSteps<-median(StepsPerDay,na.rm=TRUE)
```
Mean Steps per day is `r meanSteps` Median Steps per day is `r medianSteps`

Plotting 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
timeSeries<-tapply(activity$steps,activity$interval,mean,na.rm=TRUE)
plot(timeSeries,type="l",main="Average 5 min Interval Steps per day",xlab="time interval",ylab="steps")
maxInterval<-names(which.max(timeSeries))
```
The 5 minute interval with the max val is `r maxInterval`

```{r}
NumNa<-sum(is.na(activity$steps))
```
Number of NA values `r NumNa`

### Imputing Missing Values
Replacing missing NA values with the average value of that particular time interval

```{r}
FixedActivity<-activity
for (i in 1:nrow(FixedActivity)){
  if(is.na(FixedActivity[i,1])){
    FixedActivity[i,1]<-timeSeries[[as.character(FixedActivity[i,"interval"])]]
  }
}

```

Calculating Average Steps per day for fixed data
```{r}

StepsPerDay<-tapply(FixedActivity$steps,FixedActivity$date,sum,na.rm=TRUE)
```

Plotting Average Steps per day for fixed data

```{r fig.width=7, fig.height=6}
hist(StepsPerDay,xlab="Steps Per Day",ylab = "Number of Days",ylim=c(0,40),main="Steps Per Day")
```

calculating Mean and Median Steps per day for fixed data
```{r}
NewMeanSteps<-mean(StepsPerDay,na.rm=TRUE)
NewMedianSteps<-median(StepsPerDay,na.rm=TRUE)
```
Mean Steps per day is `r NewMeanSteps` Median Steps per day is `r NewMedianSteps`

The impact of fixing the data is that the average steps per day increased from `r meanSteps` to `r NewMeanSteps`